```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.width = 9.4, fig.height = 6)
```

## Performance Stats for MT Cars Data

`r format(Sys.Date(), format="%B %d %Y")`

An evaluation of thirty-two 1973 model year cars in terms of horsepower, fuel efficiency, engine displacement and acceleration.  Original data was published by Motor Trend magazine in 1974.

Check out the plot below that shows all four dimensions listed above.  Hover over each point to see the model and each statistic plotted.

MPG, Horsepower, and Displacement are plotted in 3D,  The color represents the quarter mile time with purple dots being the quicker cars and yellow being thw slowest.


``` {r, echo=F, message=F}

# plotly stuff for project 2

library(plotly)

d1<-mtcars
d1$Model<-row.names(d1)

plot<-plot_ly(d1, x=~d1$mpg, y=~d1$disp, z=~d1$hp, type="scatter3d", color=d1$qsec,
              mode="markers", text= ~paste(d1$Model, "Horsepower:", d1$hp, "Displacement:",
              d1$disp,"MPG:", d1$mpg, "Quarter Mile:", d1$qsec, sep="<br>"),hoverinfo="text") %>%
      layout(
              title = "Horsepower, Displacement, and Mileage for MT Cars Data",
              scene = list(
                            xaxis = list(title = "MPG"),
                            yaxis = list(title = "Displacement"),
                            zaxis = list(title = "Horsepower")
                   ))%>%
      config(displayModeBar=F)

plot
```

